The guts of the dispRity package

### 2021-03-31 inst/gitbook/06_guts.Rmd
added book entries

>>>>

#### `get.tree` `add.tree` and `remove.tree`

These functions allow to manipulate the potential tree components of `dispRity` objects.

```{r, eval = FALSE}
## Getting the tree component of a dispRity object
get.tree(disparity)

## Removing the tree
remove.tree(disparity)

## Adding a tree
add.tree(disparity, tree = BeckLee_tree)
```
